%==============================================================================
% Reduced-Sector chi-Universality in Lorentzian EC+NY Minisuperspace:
% Topology-Robust Admissibility, P-Channel Diagnostics,
% and Reduced Vacuum Orbits
%==============================================================================
\documentclass[12pt,a4paper]{article}

%------------------------------------------------------------------------------
% Packages
%------------------------------------------------------------------------------

% Fonts / encoding
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{textcomp}
\usepackage[final]{microtype}

% Math
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{mathtools}
\usepackage{bm}

% Graphics and figures
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}

% Tables
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{xurl}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcommand{\code}[1]{\path{#1}}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

% Layout and formatting
\usepackage[margin=2.5cm]{geometry}
\usepackage{setspace}
\onehalfspacing

% Misc (xcolor before hyperref)
\usepackage{xcolor}
\usepackage{enumitem}

% References and links
\definecolor{linkblue}{RGB}{0,0,180}
\usepackage[colorlinks=true,linkcolor=linkblue,citecolor=linkblue,urlcolor=linkblue]{hyperref}
\usepackage{cleveref}

% Code listings
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily\small,
  breaklines=true,
  frame=single,
  language=Python
}

% Section break
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}

%------------------------------------------------------------------------------
% Theorem environments
%------------------------------------------------------------------------------
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{remark}
\newtheorem{remark}{Remark}

%------------------------------------------------------------------------------
% Custom commands
%------------------------------------------------------------------------------
% Math shortcuts
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Sthree}{S^{3}}
\newcommand{\Tthree}{T^{3}}
\newcommand{\Nilthree}{\mathrm{Nil}^{3}}
\newcommand{\Solthree}{\mathrm{Sol}^{3}}
\newcommand{\kap}{\kappa}

% Topology bookkeeping
\newcommand{\topo}{\Sigma}
\newcommand{\Ctop}{C_{\mathrm{topology}}}
\newcommand{\Disc}{\Delta}

% Diagnostic quantities
\newcommand{\Pform}{P_{\mathrm{form}}}
\newcommand{\Pint}{P_{\mathrm{int}}}
\newcommand{\PintMX}{P_{\mathrm{int}}^{\mathrm{MX}}}
\newcommand{\QNY}{Q_{\mathrm{NY}}}
\newcommand{\thetaNY}{\theta_{\mathrm{NY}}}

% Branch labels
\newcommand{\EH}{\mathrm{EH}}
\newcommand{\AX}{\mathrm{AX}}
\newcommand{\VT}{\mathrm{VT}}
\newcommand{\MX}{\mathrm{MX}}

% Hamiltonian
\newcommand{\Ham}{\mathcal{H}}

% Geometry
\newcommand{\Vol}{\mathcal{V}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\Tr}{\mathrm{Tr}}

%------------------------------------------------------------------------------
% Title and author
%------------------------------------------------------------------------------
\title{Reduced-Sector $\chi$-Universality\\in Lorentzian EC+NY Minisuperspace:\\
Topology-Robust Admissibility, P-Channel Diagnostics,\\
and Reduced Vacuum Orbits}

\author{Muacca}

\date{}

%==============================================================================
\begin{document}
%==============================================================================

\maketitle
\begin{center}
Version: v1\\
First release: 2026-05-16
\end{center}

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
\begin{abstract}
We analyse the topology dependence of the Lorentzian Einstein--Cartan plus
Nieh--Yan (EC+NY) reduced sector across the four homogeneous three-geometries
$\Sthree$, $\Tthree$, $\Nilthree$, and $\Solthree$, restricted to the
$\alpha=0$ EC+NY reduced branch.  For $\Nilthree$ and $\Solthree$ the
treatment is confined to the isotropic-scale reduction.

In this reduced sector the Hamiltonian constraint and the torsion auxiliary
equations exhibit a topology-robust admissibility pattern: the EH, AX, and VT
branches are admissible, while the MX branch is conditionally admissible
through a real auxiliary branch.  For Pontryagin-type quantities we separate
the form-Hodge density $\Pform$, the internal-pair diagnostic $\Pint$, and the
Nieh--Yan endpoint channel $\QNY$.  The form-Hodge density $\Pform$ vanishes
exactly on the active torsion branches by block orthogonality.  The
diagnostic $\Pint$ on the MX branch carries the topology dependence in a
single coefficient, $\Ctop = -9\chi$.

Furthermore, the reduced vacuum orbit atlas on the auxiliary shell reduces to
$\dot q^{2} + \chi = 0$.

Consequently, $\chi>0$ admits no real initial data on the reduced vacuum
atlas, $\chi=0$ gives static or degenerate behaviour, and $\chi<0$ gives
monotonic expansion together with singular-approach collapse sheets.

The two relations $\Ctop=-9\chi$ and $\dot q^{2}+\chi=0$ are obtained from
independent computational routes and converge on the same scalar $\chi$;
this convergence is the content of the $\chi$-controlled topology
universality.  The results are a classification within the reduced
Lorentzian EC+NY sector; global, anisotropic, and matter-coupled extensions
are left to future work.
\end{abstract}

%------------------------------------------------------------------------------
% Main text
%------------------------------------------------------------------------------
\input{sections/sec01}   % Introduction
\input{sections/sec02}   % Lorentzian-native setup and topology conventions
\input{sections/sec03}   % Hamiltonian admissibility by topology
\input{sections/sec04}   % P-channel dictionary and topology response
\input{sections/sec05}   % chi-universality across diagnostic and reduced-orbit levels
\input{sections/sec06}   % Four-topology admissibility classification
\input{sections/sec07}   % Reduced orbit atlas and chi-sign separation
\input{sections/sec08}   % Discussion

%------------------------------------------------------------------------------
% Acknowledgments
%------------------------------------------------------------------------------
\section*{Acknowledgments}

The author acknowledges the use of the following AI tools during manuscript
preparation: Claude Opus~4.7 (Anthropic; accessed 2026-05),
Gemini~3.1 Pro (Google; accessed 2026-05), Grok~4.3 (xAI; accessed 2026-05),
and GPT-5.5 Thinking via ChatGPT (OpenAI; accessed 2026-05).
These tools were used for language editing (including Japanese--English
translation), outlining and improving exposition, drafting and reviewing
auxiliary code (scripts and pseudocode) that was subsequently tested and
validated by the author, and proposing candidate consistency checks and
alternative derivations to be independently verified by the author.

The AI tools did not determine the scientific claims of this work and were not
used to generate or modify research data or evidentiary figures.  The author
takes full responsibility for the content and for any remaining errors.

This work was developed within the informal collaborative project
\textbf{DPPU} (\textbf{D}onut-like topology, \textbf{P}lanck-scale
compactness, \textbf{P}recession dynamics, \textbf{U}niverse).

%------------------------------------------------------------------------------
% Availability and Contact
%------------------------------------------------------------------------------
\section*{Availability and Contact}

\paragraph{Code and Data Availability}
The code and supplemental data associated with this work are available at:

\begin{itemize}
  \item Zenodo: 10.5281/zenodo.20228881
  \item GitHub: \texttt{https://github.com/Muacca/DPPUv7-paper06}
\end{itemize}

They are released under the MIT License.

\paragraph{Citation}
If you use these materials, please cite the associated manuscript and Zenodo
record:

\begin{quote}
\small
Muacca, ``Reduced-Sector $\chi$-Universality in Lorentzian EC+NY
Minisuperspace: Topology-Robust Admissibility, P-Channel Diagnostics,
and Reduced Vacuum Orbits.''
\end{quote}

\paragraph{Contact}
For questions, bug reports, or collaboration inquiries:

\begin{itemize}
  \item Email: \texttt{muacca@dmwp.jp}
  \item GitHub Issues: \texttt{https://github.com/Muacca/DPPUv7-paper06/issues}
\end{itemize}

%------------------------------------------------------------------------------
% Appendices
%------------------------------------------------------------------------------
\appendix
\input{appendices/appA}  % Topology conventions, local reductions, and caveats
\input{appendices/appB}  % Tables, computational checks, and reproducibility notes
\input{appendices/appC}  % Bianchi I lite comparison and reduced-atlas scope guard

%------------------------------------------------------------------------------
% References
%------------------------------------------------------------------------------
\bibliographystyle{unsrt}

\begin{thebibliography}{99}

\bibitem{paper1}
Muacca,
``Topology-Dependent Phase Classification of Effective Potentials
in Einstein--Cartan + Nieh--Yan Minisuperspace,''
Zenodo.\ \texttt{10.5281/zenodo.18213677} (2026).

\bibitem{paper2}
Muacca,
``Structural Robustness of Isotropic $\Sthree$ Vacua in
Einstein--Cartan Minisuperspace via Chiral Equilibrium and Weyl Stability,''
Zenodo.\ \texttt{10.5281/zenodo.18815498} (2026).

\bibitem{paper3}
Muacca,
``Unified Geometric Landau EFT of Homogeneous $\Sthree\times S^{1}$
Minisuperspace in Einstein--Cartan + Nieh--Yan Theory,''
Zenodo.\ \texttt{10.5281/zenodo.19144481} (2026).

\bibitem{paper3ec}
Muacca,
``Homogeneous Three-Topology Comparison and Mode Dictionary
in Einstein--Cartan + Nieh--Yan Theory: Geometric Structure of EC--Weyl
Coupling,''
Zenodo.\ \texttt{10.5281/zenodo.19425147} (2026).

\bibitem{paper4}
Muacca,
``Euclidean Geometric Response Dictionary and Selection Rules
for Four Thurston Geometries,''
Zenodo.\ \texttt{10.5281/zenodo.19775695} (2026).

\bibitem{paper5}
Muacca,
``Lorentzian Einstein--Cartan Minisuperspace with Nieh--Yan Torsion:
Hamiltonian Branches, Pontryagin Diagnostics,
and Weyl-Source Obstructions,''
Zenodo.\ \texttt{10.5281/zenodo.20084722} (2026).

\bibitem{Hehl1976}
F.~W.~Hehl, P.~von der Heyde, G.~D.~Kerlick, and J.~M.~Nester,
``General relativity with spin and torsion: Foundations and prospects,''
Rev.\ Mod.\ Phys.\ \textbf{48}, 393--416 (1976).

\bibitem{NiehYan1982}
H.~T.~Nieh and M.~L.~Yan,
``An identity in Riemann--Cartan geometry,''
J.\ Math.\ Phys.\ \textbf{23}, 373--374 (1982).

\bibitem{Thurston1997}
W.~P.~Thurston,
\emph{Three-Dimensional Geometry and Topology, Volume 1},
edited by S.~Levy
(Princeton University Press, Princeton, NJ, 1997).

\bibitem{Scott1983}
P.~Scott,
``The geometries of 3-manifolds,''
Bull.\ London Math.\ Soc.\ \textbf{15}, 401--487 (1983).

\bibitem{EllisMacCallum1969}
G.~F.~R.~Ellis and M.~A.~H.~MacCallum,
``A class of homogeneous cosmological models,''
Commun.\ Math.\ Phys.\ \textbf{12}, 108--141 (1969).

\bibitem{BrandenbergerPeter2017}
R.~Brandenberger and P.~Peter,
``Bouncing Cosmologies: Progress and Problems,''
Found.\ Phys.\ \textbf{47}, 797--850 (2017),
arXiv:1603.05834, doi:10.1007/s10701-016-0057-0.

\bibitem{ChandiaZanelli1997}
O.~Chandia and J.~Zanelli,
``Topological invariants, instantons, and the chiral anomaly on spaces with
torsion,''
Phys.\ Rev.\ D \textbf{55}, 7580--7585 (1997).

\end{thebibliography}

%==============================================================================
\end{document}
%==============================================================================
